Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-23 paper.tex
Note in K bar chart caption that x-derivatives were not measured or computed

    \caption{Normalized mean kinetic energy transport quantities computed as
        weighted averages based on Equation~\ref{eq:K-full}. Note that directions of
        the turbulent transport terms refer to the directions of their partial
        derivatives.}

>>>>

    \caption{Normalized mean kinetic energy transport quantities computed as
        weighted averages based on Equation~\ref{eq:K-full}, omitting the
        non-measured streamwise derivatives. Note that directions of the turbulent
        transport terms refer to the directions of their partial derivatives.}
